ggalluvial: Layered Grammar for Alluvial Plots

### 2020-04-13 README.rmd
change format function params to mimic pivot functions

```{r eval=TRUE}
titanic_long <- to_lodes_form(data.frame(Titanic),
                              key = "Demographic",
                              axes = 1:3)
head(titanic_long)
ggplot(data = titanic_long,
       aes(x = Demographic, stratum = stratum, alluvium = alluvium,
           y = Freq, label = stratum)) +
  geom_alluvium(aes(fill = Survived)) +
  geom_stratum() + geom_text(stat = "stratum") +
  theme_minimal() +
  ggtitle("passengers on the maiden voyage of the Titanic",
          "stratified by demographics and survival")
```

>>>>

```{r eval=TRUE}
titanic_long <- to_lodes_form(data.frame(Titanic),
                              axes = 1:3,
                              axes_to = "Demographic")
head(titanic_long)
ggplot(data = titanic_long,
       aes(x = Demographic, stratum = stratum, alluvium = alluvium,
           y = Freq, label = stratum)) +
  geom_alluvium(aes(fill = Survived)) +
  geom_stratum() + geom_text(stat = "stratum") +
  theme_minimal() +
  ggtitle("passengers on the maiden voyage of the Titanic",
          "stratified by demographics and survival")
```
